### 2018-06-05 README.Rmd
README updates
add functional test and create error stops in significance functions

@@

# salinity

@@

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("samdchamberlain/salinity")
```

>>>>

[![Travis-CI Build Status](https://travis-ci.org/samdchamberlain/salinity_study.svg?branch=master)](https://travis-ci.org/samdchamberlain/salinity_study)

@@

# Salinity study

@@

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("samdchamberlain/salinity_study")
```
